Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-10 report/report.tex
Add more scientific sources for procedural models
Add Goetz and Ziph source

%TODO: Mention a variety of procedural methods from different sources, start by reading Müller et al and look for more references

@@

The OSM project is a wiki-like geodatabase based on Volunteered Geographical Information (VGI), meaning anyone can contribute by adding or editing features.
OSM road data and building footprints are commonly obtained by manually tracing features in commercially available satellite images.
Such images have a limit on their resolution which puts a theoretical limit on the accuracy of map features compared to their real-world equivalents
The driving force behind the availablity of VGI is, according to \textbf{(Fan et al, 2014)}, the availablity of high resolution satellite imagery to private individuals. They claim that particularily the imagery from Bing Maps, which launched in 2010, led to an increase in building information in OSM, and the positional error is largely due to the limited resolution in such satellite imagery.

@@

@@

@@

@@

\bibitem{van-oort-06}
Van Oort P.A.J. (2006). Spatial Data Quality: From Description to Application. PhD Thesis, Wageningen University.

>>>>

Shape grammer, developed by \textbf{Stiny, 1975}
Space syntax, developed by \textbf{Hillier, 1997}. Analytical method that relies on the existence of

Wayfinding
\textbf{(Peponis, Zimring and Choi, 1990)}.

@@

The OSM project is a wiki-like geodatabase based on Volunteered Geographical Information (VGI), meaning anyone can contribute by adding or editing features.
OSM road data and building footprints are commonly obtained by manually tracing features in commercially available satellite images.
Such images have a limit on their resolution which puts a theoretical limit on the accuracy of map features compared to their real-world equivalents
The driving force behind the availablity of VGI is, according to
\textbf{Goetz and Zipf, 2012},
the availablity of high resolution satellite imagery to private individuals. They claim that particularily the imagery from Bing Maps, which launched in 2010, led to an increase in building information in OSM, and the positional error is largely due to the limited resolution in such satellite imagery.

@@

\bibitem{hillier-97}
Hillier, B. (1997) Space is the Machine: A Configurational Theory of Architecture. Cambridge University Press, Cambridge, UK.

@@

\bibitem{peponis-90}
Peponis, J., Zimring, C. and Choi, Y.K. (1990). Finding the Building in Wayfinding. Environment and Behavior, Vol. 22, 555-590.

@@

\bibitem{stiny-75}
Stiny, G. (1975) Pictorial and Formal Aspects of Shapes and Shape Grammars. Birkhauser, Basel, Switzerland.

@@

\bibitem{van-oort-06}
Van Oort, P.A.J. (2006). Spatial Data Quality: From Description to Application. PhD Thesis, Wageningen University.

\bibitem{goetz-12}
Goetz, M. and Zipf, A. (2012). Towards defining a framework for the automatic derivation of 3D CityGML models from volunteered geographic information. Int. J. 3-D Inf. Model. 2012, 1, 496–507.
